### 2016-07-04 case-studies.tex

In this section, we present two case studies that demonstrate the
applicability of our reasoning approach in varied settings, and the
consequent practical utility.

>>>>

In this section, we present two case studies that demonstrate the
applicability of our reasoning approach in varied settings, and its
consequent practical utility.

### 2016-07-04 motivation.tex
Edits.

\begin{figure}
\centering
$\{\{\texttt{C}=\texttt{k} \conj \texttt{k}\ge\texttt{a1+a2}\}\}$
\begin{tabular}{l||l}
\begin{txnimpcode}
  txn$\langle$'Wd1'$\rangle${
    if (C $\ge$ a1) {
      C := C - a1
    }
  }
\end{txnimpcode}
&
\begin{txnimpcode}
  txn$\langle$'Wd2'$\rangle${
    if (C $\ge$ a2) {
      C := C - a2
    }
  }
\end{txnimpcode}
\\
\end{tabular}
$\{\{\texttt{C}=\texttt{k-a1-a2}\}\}$

@@

First, we note that the example in Fig.~\ref{fig:motiv-eg-1} is a
concurrent program, and hence is amenable to \emph{rely-guarantee}
style reasoning~\cite{rgjones}, a compositional proof technique that
allows us to reason about the behaviour of individual threads by
abstracting away interferences induced by other threads (collectively
called \emph{the environment}) into a \emph{rely} relation. In an
ordinary concurrent program, every environment step is a valid
interference in the current thread. However, in the presence of
transactions executing under various levels of weak isolation,
determining what constitutes an interference is a non-trivial problem.
For example, a \iso{Serializable} transaction admits no interference,
whereas within a transaction executing under \iso{Read Uncommitted}
isolation all interferences are valid. Between these two extremes are
various levels of isolation that admit some interferences while
prohibiting others. For example, \iso{Read Committed} isolation admits
interference of a committed transaction, but not that of an
uncommitted transaction. \iso{Snapshot Isolation} admits interference
from committed non-conflicting transactions, and so on.

>>>>

\begin{figure}
\centering
$\{\texttt{C}=\texttt{k} \conj \texttt{k}\ge\texttt{a1+a2}\}$
\begin{tabular}{l||l}
\begin{txnimpcode}
  txn$\langle$'Wd1'$\rangle${
    if (C $\ge$ a1) {
      C := C - a1
    }
  }
\end{txnimpcode}
&
\begin{txnimpcode}
  txn$\langle$'Wd2'$\rangle${
    if (C $\ge$ a2) {
      C := C - a2
    }
  }
\end{txnimpcode}
\\
\end{tabular}
$\{\texttt{C}=\texttt{k-a1-a2}\}$

@@

First, we note that the example in Fig.~\ref{fig:motiv-eg-1} is a
concurrent program, and hence is amenable to \emph{rely-guarantee}
style reasoning~\cite{rgjones}, a compositional proof technique that
allows us to reason about the behavior of individual threads by
abstracting away interferences induced by other threads (collectively
called \emph{the environment}) into a \emph{rely} relation. In an
ordinary concurrent program, every environment step is a valid
interference in the current thread. However, in the presence of
transactions executing under various levels of weak isolation,
determining what constitutes an interference is a non-trivial problem.
For example, a \iso{Serializable} transaction admits no interference,
whereas within a transaction executing under \iso{Read Uncommitted}
isolation all interferences are valid. Between these two extremes are
various levels of isolation that admit some interferences while
prohibiting others. For example, \iso{Read Committed} isolation admits
interference of a committed transaction, but not that of an
uncommitted transaction. \iso{Snapshot Isolation} admits interference
from committed non-conflicting transactions, and so on.
